HO unification from object language to meta language

### 2024-03-29 paper/main.tex
update tex

In the examples above, the first expression is a \maybeeta since $A_x$ can
reduce to $x$, the second one is not a \maybeeta since it exists no substitution
for $A_x$ such that $A_x$ reduces to $x$ and $x$ is not free in the subterm $f \appsep x$.
Eq.~\ref{eq:lamlam} is a bit more
complicated since, we have a spine of lambdas, this means that the whole term
is a \maybeeta, if the inner $\lambda$-term is an $\eta$-expansion of a term
$t$, and $t$ can be reduced to a term on the form $t' x$ where $x$ is not free
in $t'$. Indeed, eq.~\ref{eq:lamlam} is a \maybeeta under the substitution 
$\sigma = \{A \mapsto \lambda x.x, B \mapsto \lambda x. \lambda y. x\}$.

As a final remark, note that eq.~\ref{eq:lamdisc} is a \maybeeta even if $x$
occurs in the subterm $t' = f \appsep A_x$. It exists in fact a substitution
$\sigma = \{A \mapsto \lambda x.a\}$, for any constant $a$, such that $\sigma t'
= f \appsep a$ is a term where $x$ does not appears as a free variable.

We can now define more formally the two auxiliary relations needed for \maybeeta
detection:

>>>>

In the examples above, the first term is a \maybeeta since $A_x$ can
reduce to $x$ by setting $A_x = \lambda x.x$, 
the second one is not a \maybeeta since it exists no substitution
for $A_x$ such that $A_x$ reduces to $x$ and $x$ is not free in the subterm $f \appsep x$.
It is a bit more complicated to determine if eq.~\ref{eq:lamlam} a \maybeeta since,
we have a spine of lambdas, this means that the whole term
is a \maybeeta, if the inner $\lambda$-term $\lambda y.f\appsep A_x\appsep B_yx$,
is an $\eta$-expansion and, if so, we need to verify if the $\eta$-reduced 
subterm, i.e. $f \appsep A_x$, can make $\lambda x.f \appsep A_x$ an $\eta$-expansion.
Indeed, eq.~\ref{eq:lamlam} is a \maybeeta under the substitution 
$\sigma = \{A \mapsto \lambda x.x, B \mapsto \lambda x. \lambda y. x\}$.
Lastly, eq.~\ref{eq:lamdisc} is a \maybeeta even if $x$
occurs in the subterm $t' = f \appsep A_x$, since it exists a substitution
$\sigma = \{A \mapsto \lambda x.a\}$, for any constant $a$, such that $\sigma t'
= f \appsep a$ is a term where $x$ does not appears as a free variable.

We can now define more formally how \maybeeta terms are detected together with
its auxiliary functions:
